---
title: "College Scorecard Data Pull"
author: "Sven Soderborg"
output: html_document
---

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(rscorecard)
library(dotenv)
library(dplyr)

# Set working directory
setwd("C:/Users/svens/Documents/College_Outcomes")

# Load API Key
load_dot_env()
sc_key(Sys.getenv("SC_KEY"))
```

## Pull data on Utah Schools
SC_Variable | SC_Description
------------- | -------------
unitid | Unit ID for institution
instnm | Name of institution
control | 1==public, 2==private non-profit, 3==private for-profit
cipcode | Classification of instructional program code
cipfield | First two digits of cipcode - General field of study
credlev | Level of credential
ugds | Enrollment of undergraduate certificate/degree-seeking students
earn_count_wne_4yr | Number of students in the 4-year cohort working and not enrolled
earn_mdn_4yr | Average earnings of students in the 4-year
earn_count_wne_1yr | Number of students in the 1-year cohort working and not enrolled
earn_mdn_1yr | Average earnings of students in the 1-year cohort
mdcost_all | Overall median for average price (tuition + fees + room and board + other expenses + books and supplies - federal, state/local government, or institutional grant - scholarship aid)
booksupply | Estimated cost of books and supplies


```{r message=FALSE, warning=FALSE}
# Declare which vars we want from the Scorecard
sc_vars <- c("unitid", "instnm", "control", "cipcode", "ugds",
             "earn_count_wne_4yr", "earn_mdn_4yr",
             "earn_count_wne_1yr", "earn_mdn_1yr",
             "mdcost_all", "booksupply")

# Request data and add useful columns
ut_df <- sc_init() %>%
  sc_filter(stabbr == c("UT"), preddeg == 3, control != 3, credlev == 3) %>%
  sc_select_(sc_vars) %>%
  sc_year("latest") %>%
  sc_get() %>%
  mutate(cipfield = substr(cipcode, 1, 2)) %>% # Create cipfield column
  mutate(netprice = mdcost_all - booksupply) %>% # Create netcost column
  select(-mdcost_all, -booksupply) %>% # Drop mdcost_all and booksupply 
  filter(complete.cases(.)) # Drop rows with NA values


# Display first few rows of data for UofU business majors
u_bus <- ut_df %>%
  filter(unitid == 230764 & cipfield == 52) %>%
  select(instnm, cipcode,
         earn_count_wne_4yr, earn_mdn_4yr,
         earn_count_wne_1yr, earn_mdn_1yr,
         netprice)
knitr::kable(head(u_bus))
```